Using Planning to Generate Natural-Language Sentences:\\ Experiences and Challenges

### 2009-12-17 trunk/Papers/crisp-ff-10/crisp-ff.tex
fertig basierend auf *alten* beispielen

Can we design heuristics that are better at deadling with the
lifecycle of substitution nodes and distractors? The problem of not
noticing them in the initial state is present for all approaches that
are dominated by $h^+$,
e.g.\ \cite{karpas:domshlak-ijcai-09,helmert:domshlak:icaps-09}, and
is also present for the known inadmissible landmarks heuristics
\cite{richter:etal:aaai-08}. As far as known heuristics are concerned,
hope thus resides mainly in the $h^m$ family and in abstraction
heuristics. We ran a few tests with an example like the rabbit one,
except that there are 10 distractors. The Graphplan estimate for the
initial state is $4$, i.e., $h^2$ is better than $h^+$ here. Still,
$4$ is far away from the real goal distance $14$. With merge\&shrink
\cite{helmert:etal:icaps07}, {\bf \dots (malte agreed to run a test on
  modifiers-10-10-)}

The only FF technique that appears to work reasonably well is its
action pruning technique, the ``helpful actions''. While the relaxed
plan is often much too short, it appears to always contain at least
one of the actions that actually are useful, and it certainly prunes
the set of avaibale actions quite effectively. For example, in one of
the instances where EHC turns into a breadth-first search, $16875$
nodes are explored without helpful actions; with helpful actions, this
reduces to $3078$. For larger examples, the factor between the two
numbers tends to become larger. 
%{\bf use here larger version of
%  modifiers-10-10???}

>>>>

Can we design heuristics that are better at deadling with the
lifecycle of substitution nodes and distractors? The problem of not
noticing them in the initial state is present for all approaches that
are dominated by $h^+$,
e.g.\ \cite{karpas:domshlak-ijcai-09,helmert:domshlak:icaps-09}, and
is also present for the known inadmissible landmarks heuristics
\cite{richter:etal:aaai-08}. As far as known heuristics are concerned,
hope thus resides mainly in the $h^m$ family and in abstraction
heuristics. We ran a few tests with an example like the rabbit one,
except that there are 10 distractors. The Graphplan estimate for the
initial state is $4$, i.e., $h^2$ is better than $h^+$ here. Still,
$4$ is far away from the real goal distance $14$. %
%{\bf here I could use
%  differently scaled versions to see whether the distance estimate is
%  constant across the number of distractors; I would think that
%  yes}. 
With merge\&shrink \cite{helmert:etal:icaps07}, we experimented with
various settings for the parameters (number of abstractions and size
limit for each abstraction) but could not find a setting that reduced
the search nodes to less than $5000$. So, all in all, finding better
heuristic functions for this kind of problem remains a challenge.

%{\bf \dots
%  (malte agreed to run a test on modifiers-10-10-).. larger versions
%  would also be useful, to see how the search spaces develop}

The only FF technique that appears to work reasonably well is its
action pruning technique, the ``helpful actions''. While the relaxed
plan is often much too short, it appears to always contain at least
one of the actions that actually are useful, and it certainly prunes
the set of avaibale actions quite effectively. For example, in the
10-distractor test instance, $16875$ nodes are explored without
helpful actions pruning; with pruning, this reduces to $3078$. For
larger examples, the factor between the two numbers tends to become
larger. %{\bf here, again, having actual scaled examples would help}
%{\bf use here larger version of
%  modifiers-10-10???}
